The Constant-Q Transform Spectral Envelope Coefficients: A Timbre Feature Designed for Music

### 2021-05-28 IEEE SP Magazine/05-2021 - Draft/article.tex
Updated the solution section.

We make a first observation that a pitch change in the audio translates to a linear shift in the log-spectrum \cite{brown1991, brown1992}. Assuming that pitch and timbre are independent, this implies that the same musical object at different pitches would have a similar envelope but a shifted pitch component (while two different musical objects at the same pitch would have different envelopes but a similar pitch component). Assuming $X$, $E$, $P$ and $X'$, $E'$, $P'$ as the log-spectrum, envelope, and pitch component of a musical object and a pitch-shifted version of it, respectively, this is summarized in equation \ref{eq:observation1}.
\begin{equation}
\label{eq:observation1}
\begin{split}
&X = E * P \\
&X' = E' * P' \\
&\Rightarrow E \approx E'
\end{split}
\end{equation}

We make a second observation that the FT of a convolution of two functions is equal to the point-wise product of their FTs, also known as the convolution theorem \cite{proakis1995}. This implies that the FT of the log-spectrum is equal to the point-wise product of the FT of the envelope and the FT of the pitch component. Given the previous observation that the envelope is not affected by a pitch change in the audio, we conclude that the FT of the envelope is also independent from the pitch. Assuming that $\mathcal{F}(.)$ is the FT function, this is summarized in equation \ref{eq:observation2}.
\begin{equation}
\label{eq:observation2}
\begin{split}
&\mathcal{F}(X) = \mathcal{F}(E) \cdot \mathcal{F}(P) \\
&\mathcal{F}(X') = \mathcal{F}(E') \cdot \mathcal{F}(P') \\
&\Rightarrow \mathcal{F}(E) \approx \mathcal{F}(E')
\end{split}
\end{equation}

We make a final and third observation that the magnitude FT is shift-invariant \cite{proakis1995}. ...

Equation \ref{eq:observation3}.
\begin{equation}
\label{eq:observation3}
\begin{split}
&\mathcal{F}(X) = |\mathcal{F}(X)| \cdot e^{j Arg(\mathcal{F}(X))} \\
&\mathcal{F}(X) = |\mathcal{F}(X')| \cdot e^{j Arg(\mathcal{F}(X'))} \\
&\Rightarrow |\mathcal{F}(X)| \approx |\mathcal{F}(X')|
\end{split}
\end{equation}

>>>>

We make a first observation that a pitch change in the audio translates to a linear shift in the log-spectrum \cite{brown1991, brown1992}. Assuming that pitch and timbre are independent, this implies that the same musical object at different pitches would have a similar envelope but a shifted pitch component (while two different musical objects at the same pitch would have different envelopes but a similar pitch component). This is summarized in equation \ref{eq:observation1}.
\begin{equation}
\label{eq:observation1}
\begin{split}
&X = E * P \\
&X' = E' * P' \\
&\Rightarrow E \approx E'
\end{split}
\end{equation}
where $X$, $E$, $P$ and $X'$, $E'$, $P'$ represent the log-spectrum, envelope, and pitch component of a musical object and a pitch-shifted version of it, respectively.

We make a second observation that the FT of a convolution of two functions is equal to the point-wise product of their FTs, which is also known as the convolution theorem \cite{proakis1995}. This implies that the FT of the log-spectrum would be equal to the point-wise product of the FT of the envelope and the FT of the pitch component. Given the previous observation, we infer that the FT of the envelope for a musical object and a pitch-shifted version of it would be equal. This is summarized in equation \ref{eq:observation2}.
\begin{equation}
\label{eq:observation2}
\begin{split}
&\mathcal{F}(X) = \mathcal{F}(E) \cdot \mathcal{F}(P) \\
&\mathcal{F}(X') = \mathcal{F}(E') \cdot \mathcal{F}(P') \\
&\Rightarrow \mathcal{F}(E) \approx \mathcal{F}(E')
\end{split}
\end{equation}
where $\mathcal{F}(.)$ represents the FT function.

We make a final and third observation that the magnitude FT is shift-invariant \cite{proakis1995}. This implies that

Equation \ref{eq:observation3}.
\begin{equation}
\label{eq:observation3}
\begin{split}
&\mathcal{F}(X) = |\mathcal{F}(X)| \cdot e^{j Arg(\mathcal{F}(X))} \\
&\mathcal{F}(X') = |\mathcal{F}(X')| \cdot e^{j Arg(\mathcal{F}(X'))} \\
&\Rightarrow |\mathcal{F}(X)| \approx |\mathcal{F}(X')|
\end{split}
\end{equation}
where $|.|$ and $Arg(.)$ represent the modulus and argument, respectively, for a complex array.
